On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-05 main.tex
sec 4

@@

To apply the effective Nullstellensatz theorem, we first need to
determine degree bounds, separately in $\Xb$ and $\A,$ of the
polynomials in the membership relationship. We have
\[
\deg_{\Xb}\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\}\leq D,
\]
\[
\deg_{\A}  
\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\} \leq D,
\]
\[
\deg_{\Xb,T}(1-T\pjb) \leq \Dt_j +1 
\]
and
\[
\deg_{\A}(1-T\pjb) \leq \Dt_j.
\]
For each $j \in \{i,\hdots,n\},$ by \cite[Theorem 0.5]{EN}, there exists $\alpha_j \in \mathbb{Q}[\A]\setminus\{0\}$ with 
%
\begin{align*}
\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,T)g_l + B_j(\A,\Xb,T)(1-\pjb T), \\ g_l \in 
\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\},~ A_{j,l},B_j \in \mathbb{Q}[\A][\Xb][T],
\end{align*}
%
and with the degree of $\alpha_j$ upper bounded by
%
\begin{align*}
    &\left(\prod_{k=1}^{n-i+1} D\right)\Dt_j 
    + (n-i+1)\left(\Dt_j+1\right)\left(\prod_{k=1}^{n-i}D \right)D\\
    = &\left(D^{n-i+1}\right)\Dt_j+
    (n-i+1)\left(\Dt_j+1\right)\left(D^{n-i+1} \right)\\
    &\leq D^{n}\Dt_j + n\left(\Dt_j+1\right)D^{n}\\
    &=D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right).
\end{align*}
%
Now we will show that $\alpha_j$ is the only remaining denominator whose degree we need to bound. Substitute $T \leftarrow 1/\pjb$ so that 
\[
\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,1/\pjb)g_l + 0
\]
and
%
\begin{align*}
A_{j,l}(\A,\Xb,1/\pjb) 
&= \sum_{i=1}^{n_l} A_{j,l,i}(\A,\Xb,1/\pjb)\\
&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_i}}\right)\At_{j,l,i}(\A,\Xb), ~k_i \in \mathbb{Z}.
\end{align*}
%
Let $K := \max\{k_l\}$ so that 
%
\begin{align*}
    \pjb^K \alpha_j &= \pjb^K\left(\sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,1/\pjb)g_l\right)\\
    &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{K-k_{i}}\right)\At_{j,l,i}(\A,\Xb) \right)g_l \in \Q[\A][\Xb].
\end{align*}
%
which shows that $\alpha_j$ is the only remaining denominator whose degree we need to bound other than $d_j$. Note as well that
\[
\pjb^K \in \I^{\A}.
\]
Therefore 
%
\begin{align*}
\deg h_j &\leq \left(\deg \alpha_j\right)\left(\deg d_j\right)\\
    &\leq \left(D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right)\right)\Dt_j\\
    &=D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right).
\end{align*}
%
\subsection{Proof of Theorem 7.1}
%
Now we obtain
%
\begin{align*}
    \deg \Xi_i 
    &\leq \sum_{j=i}^n \deg h_j\\
    &\leq  \sum_{j=i}^n \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
    &=  (n-i+1)\left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)\\
    &\leq  n D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) .
\end{align*}
%
And therefore,  
%
\begin{align*}
    \deg& \Delta_3 \leq \sum_{i=1}^n \deg \Xi_i\\
    &\leq n^2 D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right),
\end{align*}
%
where if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in \{1,\hdots,n\},$ the extension 
\[
\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V^A)
\]

>>>>

Our next step is to give degree bounds on the coefficients appearing
in the membership equality $\pjb \in\I^\A$. This is done using
Rabinovicz's trick. Let $T$ be a new variable; applying the
Nullstellensatz in $\C(\A)[X_1,\dots,X_n,T]$, and clearing
denominators, we obtain the existence of $\alpha_j$ in
$\C[\A]\setminus\{0\}$ and $ A_{j,\ell},B_j$ in
$\C[\A][X_1,\dots,X_n][T]$, such that
\begin{align*}
\alpha_j = \sum_{\ell=1}^{n-i+1} A_{j,\ell} g_\ell + B_j (1-\pjb T),\ \  g_\ell \in 
\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\}.
\end{align*}

@@

To apply the effective Nullstellensatz theorem, we first need to
determine degree bounds, separately in $\Xb$ and $\A,$ of the
polynomials in the membership relationship. We have
\[
\deg_{\Xb}\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\}\leq D,
\]
\[
\deg_{\A}  
\left\{ 
f^\A,\frac{\partial f^\A}{\partial X_{i+1}},\hdots,\frac{\partial f^\A}{\partial X_n}
\right\} \leq D,
\]
\[
\deg_{\Xb,T}(1-T\pjb) \leq \Dt_j +1 
\]
and
\[
\deg_{\A}(1-T\pjb) \leq \Dt_j.
\]
For each $j \in \{i,\hdots,n\},$ by \cite[Theorem 0.5]{EN}, 
%
and with the degree of $\alpha_j$ upper bounded by
%
\begin{align*}
    &\left(\prod_{k=1}^{n-i+1} D\right)\Dt_j 
    + (n-i+1)\left(\Dt_j+1\right)\left(\prod_{k=1}^{n-i}D \right)D\\
    = &\left(D^{n-i+1}\right)\Dt_j+
    (n-i+1)\left(\Dt_j+1\right)\left(D^{n-i+1} \right)\\
    &\leq D^{n}\Dt_j + n\left(\Dt_j+1\right)D^{n}\\
    &=D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right).
\end{align*}
%
Now we will show that $\alpha_j$ is the only remaining denominator whose degree we need to bound. Substitute $T \leftarrow 1/\pjb$ so that 
\[
\alpha_j = \sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,1/\pjb)g_l + 0
\]
and
%
\begin{align*}
A_{j,l}(\A,\Xb,1/\pjb) 
&= \sum_{i=1}^{n_l} A_{j,l,i}(\A,\Xb,1/\pjb)\\
&= \sum_{i=1}^{n_l} \left(\frac{1}{P_j^{k_i}}\right)\At_{j,l,i}(\A,\Xb), ~k_i \in \mathbb{Z}.
\end{align*}
%
Let $K := \max\{k_l\}$ so that 
%
\begin{align*}
    \pjb^K \alpha_j &= \pjb^K\left(\sum_{l=1}^{n-i+1} A_{j,l}(\A,\Xb,1/\pjb)g_l\right)\\
    &= \sum_{l=1}^{n-i+1}\left( \sum_{i=1}^{n_l}\left(\pjb^{K-k_{i}}\right)\At_{j,l,i}(\A,\Xb) \right)g_l \in \Q[\A][\Xb].
\end{align*}
%
which shows that $\alpha_j$ is the only remaining denominator whose degree we need to bound other than $d_j$. Note as well that
\[
\pjb^K \in \I^{\A}.
\]
Therefore 
%
\begin{align*}
\deg h_j &\leq \left(\deg \alpha_j\right)\left(\deg d_j\right)\\
    &\leq \left(D^n\left(\Dt_j + n\left(\Dt_j+1\right) \right)\right)\Dt_j\\
    &=D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right).
\end{align*}
%
\subsection{Proof of Theorem 7.1}
%
Now we obtain
%
\begin{align*}
    \deg \Xi_i 
    &\leq \sum_{j=i}^n \deg h_j\\
    &\leq  \sum_{j=i}^n \left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right) \\
    &=  (n-i+1)\left( D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) \right)\\
    &\leq  n D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right) .
\end{align*}
%
And therefore,  
%
\begin{align*}
    \deg& \Delta_3 \leq \sum_{i=1}^n \deg \Xi_i\\
    &\leq n^2 D^n\Dt_j\left(\Dt_j + n\left(\Dt_j+1\right) \right),
\end{align*}
%
where if $A \in \C^{n^2} - \Delta_3$ then, for each $i \in \{1,\hdots,n\},$ the extension 
\[
\C[\textbf{X}_{\leq i-1}]\rightarrow\C[\textbf{X}]/\frak{I}(\pi_i,V^A)
\]
